Accuracy and precision of zero-heat-flux temperature monitoring

### 2019-12-05 manuscript/manuscript.Rmd
word doc formatted to template

---
title: "Accuracy and precision of zero-heat-flux temperature monitoring: A systematic review and meta-analysis"
author:
- name: Aaron Conway
  affiliation: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: aaron.conway@utoronto.ca
  url: https://www.aaronconway.info
- name: Megan Bittner
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
- name: Dan Phan
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
- name: Navpreet Kamboj
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: navpreet.kamboj@mail.utoronto.ca
- name: Kristina Chang
  affiliation: Toronto General Hospital, UHN
- name: Peter Collins
  affiliation: Toronto General Hospital, UHN
- name: Elizabeth Tipton
  affiliation: Department of Statistics, Northwestern University
- name: Matteo Parotto
  affiliation: Toronto General Hospital, UHN
# date: "`r Sys.Date()`"
repository_url: https://github.com/awconway/zhf-review
twitter:
  creator: "@aw_conway"
bibliography: bibliography.bib
csl: anesthesiology.csl
output: word_document
# output: distill::distill_article
params:
  distill: FALSE
  word: TRUE
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(include=FALSE,
                      echo=FALSE, warning=FALSE, message=FALSE)
```

```{r conditional_title_page, results='asis', include=params$word}
cat("
## Author information

<p>Aaron Conway PhD^1,2,3^
<p>Megan Bittner BSc^2^
<p>Dan Phan BSc^2^
<p>Navpreet Kamboj BScN^2^
<p>Kristina Chang MScN^4^
<p>Peter Collins MStatistics^4^
<p>Elizabeth Tipton PhD^5^
<p>Matteo Parotto MD^4^

<p>^1^ Peter Munk Cardiac Centre, University Health Network
<p>^2^Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
<p>^3^School of Nursing, Queensland University of Technology (QUT)
<p>^4^Toronto General Hospital, UHN
<p>^5^Department of Statistics, Northwestern University

## Corresponding author

Dr Aaron Conway BN (Hons) PhD
RBC Chair in Cardiovascular Nursing Research | Peter Munk Cardiac Centre | Toronto General Hospital | University Health Network
Clinician Investigator | Toronto General Hospital Research Institute | University Health Network
Assistant Professor | Lawrence S. Bloomberg Faculty of Nursing | University of Toronto

585 University Ave, 4NU - 476
Toronto, ON  M5G 2N2

e. aaron.conway@utoronto.ca  | t. (416) 946-7112

## Declarations

@@

")
```

```{r echo=FALSE, include=FALSE}
library(magrittr)
source("loa_maker.R")
source("meta.R")
```

```{r load-data, include=FALSE}
data <- readxl::read_xlsx(here::here("manuscript", "data", "zhf_extracted.xlsx"))
```

@@

Zero-heat-flux thermometers are non-invasive devices that can be used to continuously monitor temperature. These devices are increasingly being used to substitute for invasive core temperature measurement during surgery and in critical care. The aim of this review was to determine the accuracy and precision of zero-heat-flux temperature measurements.

@@

</blockquote>
</div>

## Introduction

@@

Sixteen studies were included (Figure \@ref(fig:fig-1)). Two studies reported only in abstract form were not included and assigned as 'studies awaiting classification' because there was insufficient information provided.

```{r fig-1, fig.align="center", fig.cap="PRISMA Flow Diagram", echo=FALSE, fig.width=5.5, fig.path="", include=params$distill}
# https://github.com/awconway/ggprisma
ggprisma::ggprisma(retrieved = 130, included = 16, duplicates = 35, full_text = 22, wrong_intervention = 4, wrong_comparator = 2, wrong_design = 1, awaiting_classification = 2)
```

@@

A graphical overview of the findings for the primary analysis is presented in Figure \@ref(fig:fig-2). The pooled estimate for the mean bias between zero-heat-flux and core temperature measurements was `r primary$bias_mean`°C. The population limits of agreement, which take into consideration the between-study heterogeneity and sampling error, were wide, spanning from `r primary$CI_L_rve`°C to `r primary$CI_U_rve`°C (`r primary$Measurements` measurements; `r primary$Participants` participants; `r primary$Studies` studies). The quality of evidence for the primary comparison was downgraded to low quality due to concerns about study limitations and inconsistency. Population limits of agreement for the sensitivity analysis restricted to studies rated as having low risk of bias across all the domains of the QUADAS-2 were similar to the primary analysis (`r low_risk$Measurements` measurements; `r low_risk$Participants` participants; `r low_risk$Studies` studies). The mean bias was again `r low_risk$bias_mean`°C with population limits of agreement spanning from `r low_risk$CI_L_rve`°C to `r low_risk$CI_U_rve`°C. A further sensitivity analysis excluding studies that received industry funding revealed population limits of agreement that were considerably wider than the primary analysis (`r conflict$CI_L_rve`°C to `r conflict$CI_U_rve`°C). The GRADE rating for this sensitivity was downgraded to low quality though, due to concerns about study limitations, inconsistency and imprecision.

```{r fig-2, preview=TRUE, layout="l-screen-inset", fig.align="center", fig.cap="Graphical overview of findings for the primary analysis", echo=FALSE, fig.path="", include=params$distill}
knitr::include_graphics("gofer_core.png")
```

@@

<script src="https://hypothes.is/embed.js" async></script>

```{r  conditional_references, include=params$word, results='asis'}
cat("# References")
```
<div id="refs"></div>

```{r  conditional_figure_legend, include=params$word, results='asis'}
cat("# Figure legend

>>>>

---
title: "Accuracy and precision of zero-heat-flux temperature monitoring"
subtitle: A systematic review and meta-analysis
description: "A systematic review and meta-analysis"
# author:
# - name: Aaron Conway
#   affiliation: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
#   email: aaron.conway@utoronto.ca
#   url: https://www.aaronconway.info
# - name: Megan Bittner
#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
# - name: Dan Phan
#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
# - name: Navpreet Kamboj
#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
#   email: navpreet.kamboj@mail.utoronto.ca
# - name: Kristina Chang
#   affiliation: Toronto General Hospital, UHN
# - name: Peter Collins
#   affiliation: Toronto General Hospital, UHN
# - name: Elizabeth Tipton
#   affiliation: Department of Statistics, Northwestern University
# - name: Matteo Parotto
#   affiliation: Toronto General Hospital, UHN
# date: "`r Sys.Date()`"
# repository_url: https://github.com/awconway/zhf-review
# twitter:
#   creator: "@aw_conway"
bibliography: Extras/bibliography.bib
csl: Extras/anesthesiology.csl
author:
  - Aaron Conway PhD:
      email: aaron.conway@utoronto.ca
      institute: [PMCC, LBFON, QUT]
      correspondence: true
  - Megan Bittner BSc:
      institute: [LBFON]
      correspondence: false
  - Dan Phan BSc:
      institute: [LBFON]
      correspondence: false
  - Kristina Chang MScN:
      institute: [TGH]
      correspondence: false
  - Elizabeth Tipton PhD:
      institute: [NW]
      correspondence: false
  - Matteo Parotto MD:
      institute: [TGH]
      correspondence: false
institute:
  - PMCC: Peter Munk Cardiac Centre, University Health Network
  - LBFON: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  - QUT: School of Nursing, Queensland University of Technology (QUT)
  - TGH: Toronto General Hospital, UHN
  - NW: Department of Statistics, Northwestern University
output:
  bookdown::word_document2:
    reference_docx: Extras/manuscript_template.docx
    pandoc_args:
      - --csl=Extras/anesthesiology.csl
      - --lua-filter=Extras/scholarly-metadata.lua
      - --lua-filter=Extras/author-info-blocks.lua
#output: distill::distill_article
params:
  distill: FALSE
  word: TRUE
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(include=FALSE,
                      echo=FALSE, warning=FALSE, message=FALSE)
library(dplyr)
library(ggprisma) # https://github.com/awconway/ggprisma
library(gt)
library(knitr)
library(magrittr)
source("R/loa_maker.R")
source("R/meta.R")
```

```{r conditional_title_page, results='asis', include=params$word}
cat("
## Declarations

@@

##### Page break

")
```
```{r load-data, include=FALSE}
data <- readxl::read_xlsx(here::here("manuscript", "data", "zhf_extracted.xlsx"))
```

@@

Zero-heat-flux thermometers provide clinicians with the ability to continuously and non-invasively monitor body temperature. These devices are increasingly being used to substitute for invasive core temperature measurement during surgery and in critical care. The aim of this review was to determine the accuracy and precision of zero-heat-flux temperature measurements.

@@

</blockquote>
</div>
```{r conditional_page_break, results='asis', include=params$word}
cat("
##### Page break
")
```
## Introduction

@@

Sixteen studies were included (Figure 1). Two studies reported only in abstract form were not included and assigned as 'studies awaiting classification' because there was insufficient information provided.

```{r fig-1, fig.align="center", fig.cap="PRISMA Flow Diagram", echo=FALSE, fig.width=5.5, fig.path="figures/", include=params$distill, eval=params$distill}
# https://github.com/awconway/ggprisma
ggprisma::ggprisma(retrieved = 130, included = 16, duplicates = 35, full_text = 22, wrong_intervention = 4, wrong_comparator = 2, wrong_design = 1, awaiting_classification = 2)
```

@@

A graphical overview of the findings for the primary analysis is presented in Figure 2. The pooled estimate for the mean bias between zero-heat-flux and core temperature measurements was `r primary$bias_mean`°C. The population limits of agreement, which take into consideration the between-study heterogeneity and sampling error, were wide, spanning from `r primary$CI_L_rve`°C to `r primary$CI_U_rve`°C (`r primary$Measurements` measurements; `r primary$Participants` participants; `r primary$Studies` studies). The quality of evidence for the primary comparison was downgraded to low quality due to concerns about study limitations and inconsistency. Population limits of agreement for the sensitivity analysis restricted to studies rated as having low risk of bias across all the domains of the QUADAS-2 were similar to the primary analysis (`r low_risk$Measurements` measurements; `r low_risk$Participants` participants; `r low_risk$Studies` studies). The mean bias was again `r low_risk$bias_mean`°C with population limits of agreement spanning from `r low_risk$CI_L_rve`°C to `r low_risk$CI_U_rve`°C. A further sensitivity analysis excluding studies that received industry funding revealed population limits of agreement that were considerably wider than the primary analysis (`r conflict$CI_L_rve`°C to `r conflict$CI_U_rve`°C). The GRADE rating for this sensitivity was downgraded to low quality though, due to concerns about study limitations, inconsistency and imprecision.

```{r fig-2, preview=TRUE, layout="l-screen-inset", fig.align="center", fig.cap="Graphical overview of findings for the primary analysis", echo=FALSE, fig.path="", include=params$distill}
knitr::include_graphics("figures/gofer_core.png")
```

@@

```{r  conditional_references, include=params$word, results='asis'}
cat("##### Page break

# References")
```
<div id="refs"></div>

```{r  conditional_figure_legend, include=params$word, results='asis'}
cat("##### Page break

# Figure legend
